---
title: "spice-girls"
author: "Manuel Alcalá Kovalski"
date: "12/14/2021"
output: html_document
---
---
title: "Spice Girls"
date: 2021-12-14
output: html_output
---

# TidyTuesday


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_light())
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}
tt <- tt_load("2021-12-14")
```



# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}
tt %>% 
  map(glimpse) %>% 
  kableExtra::kbl()
```



```{r Wrangle}
lyrics <- tt$lyrics
lyrics_by_member <- lyrics %>% 
  separate_rows(section_artist, sep = ", | & | with | and ") %>%
  mutate(
    section_artist = str_remove_all(section_artist, "\\(|\\)|\\{|\\}")
  ) %>% 
  filter(section_artist %in% c("Sporty", "Baby", "Scary", "Ginger", "Posh"))
lyrics_by_member %>% 
  count(section_artist, sort = TRUE)
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
library(tidytext)
p <- lyrics_by_member %>% 
  unnest_tokens(word, line) %>% 
  count(section_artist, word) %>% 
  bind_tf_idf(word, section_artist, n) %>% 
  group_by(section_artist) %>% 
  slice_max(tf_idf, n = 6) %>% 
  ungroup() %>% 
  mutate(
    section_artist = factor(section_artist,
                            levels = c("Sporty", "Baby", 
                                       "Scary", "Ginger", "Posh")),
    word = reorder_within(word, tf_idf, section_artist)
    ) %>% 
  ggplot(aes(tf_idf, word, fill = section_artist)) +
  geom_col(show.legend = FALSE) +
  scale_y_reordered() +
  facet_wrap(vars(section_artist), scales = "free_y") +
  labs(title = "Tf-idf analysis of lyrics by member of Spice Girls",
       caption = "Source: Genius")
p
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}
# This will save your most recent plot
ggsave("image/spice_girls.png", p, width = 6, height = 4)
```
